\pdfbookmark[-1]{Title Page}{titlepage}

\maketitle
\makeatletter

\noindent Coordinator: \@modulecoord \\
Lecturers: \@modulelecturers \\
TAs: \@moduletas
\makeatother

\textbf{Lecture Timetable:}\\
36 lectures, 3 per week during Semester 1
\begin{itemize}
    \item[] Monday 10am Room 216/Zoom
    \item[] Wednesday 10am Room 216/Zoom
    \item[] Friday 9am Room 216/Zoom
\end{itemize}
Weeks 1--4 §8.0 External Flow Dr. K. Nolan\\
Weeks 5--8 §9.0 Compressible Flow Dr. K. Nolan\\
Weeks 9--12 Turbomachinery Dr. W. Smith\\
\textbf{Laboratory:}
2 laboratory exercises each of 2 hour duration
\begin{itemize}
    \item[] Wednesday 3pm Room 005
    \item[] Thursday 3pm Room 005
\end{itemize}
Laboratory exercises support section 8.0 \& 9.0
\begin{enumerate}
    \item External Flow: Wind Tunnel Testing
    \item Compressible Flow: De Laval Nozzle Testing
\end{enumerate}

\textbf{Assessment:}\\
Midterm In-Class Test:
\begin{itemize}
    \item[] Friday 25th October 2020 \hfill 15\%
\end{itemize}
Laboratory — Express format
\begin{itemize}
    \item[] Full report (due Friday 6th November 2020) \hfill10\%
    \item[] Short report (due Friday 4th December 2019) \hfill5\%
\end{itemize}
\margintext{No laboratory marks will be given if a student fails to sign in at a laboratory.}
Final Open Book Examination:
\begin{itemize}
    \item[] During weeks 14 and 15 \hfill70\%
\end{itemize}
\textbf{Recommended Texts:}\\
``Fluid Mechanics'' -- Frank M. White\\
McGraw-Hill International Editions, 5th Edition\\
``Fundamentals of Fluid Mechanics'' -- Bruce .R. Munson, Donald. F. Young and Theodore. H. Okiishi\\
John Wiley \& Sons, 5th Edition\\
``Introduction to Fluid Mechanics'' -- Edward. J. Shaughnessy Jr, Ira. M. Katz and James. P. Schaffer\\
Oxford University Press, 1st Edition